New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-07-31 paper/comments_to_reviewers.tex
wip

\begin{document}

		%\title{Cover Letter}
		%\maketitle

		\begin{letter}{}

			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.

		We propose new algorithms for those two problems after proving that if the number of given ellipses is constant, an optimal solution is contained in a polynomial-sized set of solutions, transforming both problems in combinatorial optimization problems.

		We show that significant advances were accomplished both in theory and in practice by our work, and we believe that our manuscript is a strong match for this journal as, besides dealing with an optimization problem that has not been vastly studied, the most recent paper on this subject is published here.

		\closing{On behalf of the authors and with our best regards,}
			\end{letter}
		%\section*{References}
		%% New version of the num-names style
		%\bibliographystyle{elsarticle-num}
		%\bibliography{../references}

>>>>

\begin{document}
\begin{letter}{Comments to reviewers}
			\opening{Dear Steffen Rebennack\\Editor of EJOR}

			Thanks for the great opportunity of having our work reviewed by EJOR's editorial board, which provided great comments and suggestions that surely enhanced the quality of our work.

			Besides the modifications in the text to address the issues raised by the reviewers, we have also made some small corrections and changes of notation on our own. These modifications were mostly suggestions given by the board that reviewed the dissertation from which this paper derived. In the text, we annoted these changes with the color {\color{blue}blue}.

			The other modifications were made to address the issues raised by the reviewers, and we highlighted them as follows:

			\begin{itemize}
				\item The {\color{Red} red} highlights are corrections concerning the points made by reviwer \#1.

				\item The {\color{Green} green} highlights are corrections concerning the points made by reviwer \#2.

				\item The {\color{Orange} orange} highlights are corrections concerning points made by both reviewers.
			\end{itemize}

			Please see in the next pages the answers to both reviewers.

			\closing{On behalf of the authors and with our best regards,}
\end{letter}
	\input{answer_rev_1.tex}
	\input{answer_rev_2.tex}
